Open-source landscape for 3D CSEM modelling

### 2020-04-28 manuscript/Manuscript.tex
First Marlim figures

%
\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
  out once we all submitted the final versions of the results.}}{
  \centering
\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
  \toprule
  %
  Code & {CPU} & \#Procs & RAM     & \#Cells \\
       & {(s)} &         & {(GiB)} &         \\
  \midrule
  %
  \custem & 0.0 & 24 & 0.0 & 0 \\
  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
  \petgem & 0.0 & 48 & 0.0 & 0 \\
  \simpeg & 0.0 &    & 0.0 & 0 \\
  %
  \bottomrule
\end{tabular}}%
%

@@

>>>>

%
\plot*{model-marlim}{width=\textwidth}{
  Needs improvements.
}
%

%
\plot*{results-marlim}{width=\textwidth}{
  This is one heck of a figure. Just an idea, please make suggestions how to
  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
  data is a copy of \emg3d data).
}
%

%
\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
  out once we all submitted the final versions of the results.}}{
  \centering
\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
  \toprule
  %
  Code & {CPU} & \#Procs & RAM     & \#Cells \\
       & {(s)} &         & {(GiB)} &         \\
  \midrule
  %
  \custem & 0.0 &  0 & 0.0 & 0 \\
  \emg3d  & 0.0 &  0 & 0.0 & 0 \\
  \petgem & 0.0 &  0 & 0.0 & 0 \\
  \simpeg & 0.0 &  0 & 0.0 & 0 \\
  %
  \bottomrule
\end{tabular}}%
%

The three meaningful responses for node-based marine CSEM: Inline Ex and
Broadside Ex and Ey.

@@

\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
and Conclusion collaboratively at the same time?}
